Classless Java

### 2015-11-13 paper/paper.tex
latex table
LIPICS format

%\documentclass[preprint]{sigplanconf}

\documentclass[preprint]{llncs}
\input{def}

\usepackage{color}

\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{pstricks,pst-node,pst-tree}
\usepackage{theorem}
%% \usepackage{mathpartir}
\usepackage{bbm}
\usepackage{pgf}
\usepackage{multirow}

@@

\pagestyle{plain}

%{\theorembodyfont{\sffamily} \newtheorem{theorem}{Theorem}}
%{\theorembodyfont{\sffamily} \newtheorem{lemma}{Lemma}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newenvironment{proof}{\textbf{Proof:\hspace{4mm}}}{$\Box$}
\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
\newcommand{\hl}[1]{\textcolor{red}{#1}}
\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
\newcommand\haoyuan[1]{\authornote{haoyuan}{cyan}{#1}}

@@

\begin{comment}
\author{Bruno C. d. S. Oliveira and Yanlin Wang}
\institute{The University of Hong Kong\\
\email{\{bruno,ylwang\}@cs.hku.hk}\\
\authorrunning{Bruno Oliveira and Yanlin Wang}} % abbreviated author list (for running head)
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Classless Java}
%%\subtitle{Solving The Expression Problem with Covariant Return Types}
%% Poor Man's Family Polymorphism

\maketitle

@@

\bibliographystyle{splncs}
\bibliography{paper}

>>>>

%\documentclass[preprint]{sigplanconf}
%\documentclass[preprint]{llncs}
\documentclass[a4paper,UKenglish]{lipics}

\input{def}

\usepackage{microtype}%if unwanted, comment out or use option "draft"
\usepackage[table,xcdraw]{xcolor}
\usepackage{color}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{url}
\usepackage{pstricks,pst-node,pst-tree}
\usepackage{theorem}
%% \usepackage{mathpartir}
\usepackage{bbm}
\usepackage{pgf}
\usepackage{multirow}

@@

%\pagestyle{plain}

%{\theorembodyfont{\sffamily} \newtheorem{theorem}{Theorem}}
%{\theorembodyfont{\sffamily} \newtheorem{lemma}{Lemma}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newenvironment{proof}{\textbf{Proof:\hspace{4mm}}}{$\Box$}
\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
%\newcommand{\hl}[1]{\textcolor{red}{#1}}
\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
\newcommand\haoyuan[1]{\authornote{haoyuan}{cyan}{#1}}

@@

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Classless Java}
\titlerunning{Classless Java}

\author[1]{John Q. Open}
\author[2]{Joan R. Access}
\affil[1]{Dummy University Computing Laboratory\\
  Address, Country\\
  \texttt{open@dummyuni.org}}
\affil[2]{Department of Informatics, Dummy College\\
  Address, Country\\
  \texttt{access@dummycollege.org}}
\authorrunning{J.\,Q. Open and J.\,R. Access} 
% mandatory. First: Use abbreviated first/middle names. Second (only in severe
% cases): Use first author plus 'et. al.'

\Copyright{John Q. Open and Joan R. Access}
% mandatory, please use full first names. LIPIcs license is "CC-BY";
% http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification -- please refer to
  \url{http://www.acm.org/about/class/ccs98-html}}
% mandatory: Please choose ACM 1998 classifications from
% http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of
% Computation".
\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\serieslogo{}%please provide filename (without suffix)
\volumeinfo%(easychair interface)
  {Billy Editor and Bill Editors}% editors
  {2}% number of editors: 1, 2, ....
  {Conference title on which this volume is based on}% event
  {1}% volume
  {1}% issue
  {1}% starting page number
\EventShortName{}
\DOI{10.4230/LIPIcs.xxx.yyy.p}% to be completed by the volume editor
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle

@@

%\bibliographystyle{splncs}
\bibliographystyle{plain}
\bibliography{paper}

### 2015-11-13 paper/sections/RelatedWork.tex
LIPICS format

 To fight those limitations, an algebra of mixin operators is introduced~\cite{CMS elena zucca davide ancona}, but this raised the complexity of the approach, especially when constructors and fields are considered~\cite{Ecoop FJigsaw marco}.

@@

\subsection{Multiple Inheritance in Java}
Since Java 8 default methods are introduced, which enables concrete method
implementation to be defined (via the \textbf{default} keyword) inside
interfaces. Since Java supports implementation of multiple interfaces (instead of extension of a single
class), the introduction of default methods opens the gate for various flavours of multiple
inheritance in Java, using interfaces. 
Former work by Bono.et. al.~\cite{bono14}.
provides details on mimicking traits~\cite{sharly thesis} through interfaces.

>>>>

 To fight those limitations, an algebra of mixin operators is introduced~\cite{CMS-elena-zucca-davide-ancona}, but this raised the complexity of the approach, especially when constructors and fields are considered~\cite{Ecoop-FJigsaw-marco}.

@@

\subsection{Multiple Inheritance in Java}
Since Java 8 default methods are introduced, which enables concrete method
implementation to be defined (via the \textbf{default} keyword) inside
interfaces. Since Java supports implementation of multiple interfaces (instead of extension of a single
class), the introduction of default methods opens the gate for various flavours of multiple
inheritance in Java, using interfaces. 
Former work by Bono.et. al.~\cite{bono14}.
provides details on mimicking traits~\cite{sharly-thesis} through interfaces.
